Regional-scale Base-flow Index of Gauged and Ungauged Basins in Drylands

### 2024-11-29 index.qmd
new words
updating trend stuff

@@

@@

| Classification Group         |   n | n_pos | n_neg | perc_pos | perc_neg |
|:-----------------------------|----:|------:|------:|---------:|---------:|
| Climate - Monsoon Dominated  |  94 |    10 |    23 |    0.106 |    0.245 |
| Climate - Snowmelt Dominated | 150 |    19 |    17 |    0.127 |    0.113 |
| PhysRegion - Basin&Range     | 190 |    26 |    33 |    0.137 |    0.174 |
| PhysRegion - CO Plateau      |  54 |     3 |     7 |    0.056 |    0.130 |
| Climate - Warm-Wet           |  31 |     3 |     6 |    0.097 |    0.194 |
| Climate - Warm-Dry           |  81 |    15 |    16 |    0.185 |    0.198 |
| Climate - Cool-Wet           |  83 |     6 |    11 |    0.072 |    0.133 |
| Climate - Cool-Dry           |  49 |     5 |     7 |    0.102 |    0.143 |
| Slope - High                 | 111 |    12 |    15 |    0.108 |    0.135 |
| Slope - Low                  | 133 |    17 |    25 |    0.128 |    0.188 |

>>>>

These trends were produced using a Mann-Kendall test for monotonic trends. This test expects that the data is non-parametric and that the observations are not autocorrelated over time. Observations of BFI at 4 streamgages show significant autocorrelation, though only one streamgage (09486500 - Santa Cruz River at Cortaro, AZ) indicated a significant trend in BFI. Due to this autocorrelation, the streamgage was removed from the trend analysis as the autocorrelation may inflate the variance of the Mann-Kendall statistic leading to an over/underestimate of the trend (CITATION).

@@

Trends in BFI over the period of record for each streamgage in this analysis are illustrated in @fig-instrumented-trend and @tbl-trends .

@@

| Classification Group         |   n | n_pos | n_neg | perc_pos | perc_neg |
|:-----------------------------|----:|------:|------:|---------:|---------:|
| Climate - Monsoon Dominated  |  94 |     9 |    23 |    0.096 |    0.245 |
| Climate - Snowmelt Dominated | 150 |    19 |    17 |    0.127 |    0.113 |
| PhysRegion - Basin&Range     | 190 |    25 |    33 |    0.132 |    0.174 |
| PhysRegion - CO Plateau      |  54 |     3 |     7 |    0.056 |    0.130 |
| Climate - Warm-Wet           |  31 |     2 |     6 |    0.065 |    0.194 |
| Climate - Warm-Dry           |  81 |    15 |    16 |    0.185 |    0.198 |
| Climate - Cool-Wet           |  83 |     6 |    11 |    0.072 |    0.133 |
| Climate - Cool-Dry           |  49 |     5 |     7 |    0.102 |    0.143 |
| Slope - High                 | 111 |    12 |    15 |    0.108 |    0.135 |
| Slope - Low                  | 133 |    16 |    25 |    0.120 |    0.188 |
